Delay d'ETRE: Explict Temporal Ratios Lead to Impatience

### 2015-12-15 paper/paperintro.tex
describe losses

\begin{abstract}
	When selecting a shipping speed on Amazon we are faced with a choice between getting our package sooner but paying more money, or getting our package later and paying less money. 
	The general phenomenon underlying our expedited shipping is impatience, we want good things immediately and we must be compensated for waiting. 
	Previous research on intertemporal framing has shown that displaying times as dates -- January 23rd -- as opposed to delays -- 6 weeks -- increases patience. 
	Other research has shown that people use both differences and ratios of time in intertemporal choices. 
%	These two results suggest that framing times as ratios alters patience. 
%	In three experiments I manipulate the temporal presentation from the standard -- 1 day versus 5 days --  to making the ratio explicit -- 1 day or 5 times as long.  
	Across three experiments I show that making temporal ratios explict leads to differing levels to increase impatience in standard  intertemporal choices framed as gains, intertemporal choices framed as losses, and for an explicit shipping scenario. 
	Taken together these results suggest that framing delays as ratios leads to greater impatience.

%
%	People use ratios in everyday life -- intertemporal choices are no different, 
%	recent cognitive models of intertemporal choice show that people calculate ratios of both money and time. 
%	These models account for diminishing impatience -- when items are moved into the future, people are more patient. 
%	Our goal is twofold: 1) to show that previous models of intertemporal choice do not properly account for temporal ratios and present a conceptual model of time discounting, and  2) by explicitly manipulating how people use ratios of time, we can alter how people make intertemporal choices. 
%	This leads to novel predictions for how to optimally frame intertemporal choices to induce either patience or impatience. 
%	Further we show that in a hypothetical shipping scenario that when temporal ratios are explicit, people are more impatient.

@@

How the monetary and temporal aspects of an intertemporal choice are framed lead to varying degrees of patience.
Further, recent models of intertemporal choice have posited that people use ratios in intertemporal choices \cite{Read2013, MarzilliEricson2015}. 
%For instance \citeA{Read2013} found that by making ratios in the 
However, to the best of my knowledge, no study has investigated how explicitly framing time as a ratio can alter patience.
Further although shipping scenarios are a form of intertemporal choice, they differ from how most studies operationalize intertemporal choices. 
Across 3 studies I show that by making ratios explicit people are more impatient in intertemporal choices. 
%Further we show that by making the ratios between times explicit we can induce a higher reliance on ratios.
This result holds for intertemporal choices framed as gains, losses, and in an explicit shipping scenario. 
As opposed to other studies which showed that reframed times as dates increases patience, framing times as ratios decreases patience.
Firms wanting to decrease patience in their consumers may want to frame intertemporal choices as ratios as opposed to delays.

%If the temporal ratio is explicit people are more impatient than when the ratio is implicit.

%
%There are subtle ways in which the presentation of time can alter patience. 
%For instance people are more impatient when delays are calendar dates as opposed to delays into the future \cite{Read2005}. 
%Marketers have used temporal frames in shipping scenarios.
%For example as opposed to stating that you will receive your package in 2 weeks, Amazon sometimes states that you receive your package on January 23rd. 
%As per \citeA{Read2005} this frame will increase patience.

%Many of our daily choices involve making decisions involving time in some respect, often taking the form of a the tradeoff between receiving something of smaller value now and receiving something of larger value in the future. 
%For instance when a consumer selects a shipping speed when shopping online they are making an intertemporal choice.
%These decisions require consumers to, perhaps implicitly, calculate how much waiting for the slower shipping speed is worth.

%Firms could, however, prefer that a consumer is impatient when choosing a shipping speed. 
%If a firm's inventory is low on a particular item they may not profit from the extra cost that it takes to expedite shipping, however if their inventory is high they may want to nudge consumers to ship their items faster. 
%It is important to understand what variables consumers are using and how they are making intertemporal choices to create robust and adaptive choice environments. 
%This understanding how to optimally display information leads to novel predictions for how to frame shipping speeds. 
%
%Recent models of intertemporal choice have posited that people use ratios in intertemporal choices [ITCH, DRIFT]. 
%Across [] studies we show that how people make intertemporal choices is dependent on how they perceive ratios. 
%Further we show that by making the ratios between times explicit we can induce a higher reliance on ratios. 
%If the temporal ratio is explicit people are more impatient than when the ratio is implicit.

@@

@@

%Study 2 extends the results of Study 1 to losses. 
%Although most intertemporal choice studies use gains, a large number of real world intertemporal choices involve losses \cite{Hardisty2013}. 
%For instance waiting to pay off your credit card incurs greater losses if you wait -- the compounding interest -- than if pay it off immediately.
%Intertemporal choices framed as lossed measured in the lab take the form of choices between ``Pay \$100 immediately'' and  ``Pay \$110 in 6 months'' \cite{Hardisty2015}.
%Further most studies investigating framing effects on intertemporal choices are restricted to the domain of gains. 
%Study 2 investigates how framing times as ratios leads to decreased patience in losses. 
%
%Study 3 extends the results from Study 1 and Study 2 to intertemporal choices explicitly framed as shipping scenarios.
%Shipping scenarios are typically displayed as a choice between ``Receive your items in 2 days and pay \$8'' and ``Receive your items in 10 days and pay \$4''
%Although choosing a shipping speed is similar to the previous intertemporal choices there is a subtle, yet possibly significant difference between the two.
%Shipping decisions can be thought of as \textit{paying more now to receive an item sooner} whereas the intertemporal choices shown in Study 2 can be thought of as \textit{paying something smaller now to avoid paying something larger later}.
%This difference in choices  
%

@@

>>>>

\begin{abstract}
	When selecting a shipping speed on Amazon we are faced with a choice between getting our package sooner but paying more money, or getting our package later and paying less money. 
	The general phenomenon underlying our expedited shipping is impatience, we want good things immediately and we must be compensated for waiting. 
	Previous research on intertemporal framing has shown that displaying times as dates -- January 23rd -- as opposed to delays -- 6 weeks -- increases patience. 
	Other research has shown that people use both differences and ratios of time in intertemporal choices. 
	Across three experiments I show that making temporal ratios explict leads to differing levels to increase impatience in standard  intertemporal choices framed as gains, intertemporal choices framed as losses, and for an explicit shipping scenario. 
	Taken together these results suggest that framing delays as ratios leads to greater impatience.

@@

How the monetary and temporal aspects of an intertemporal choice are framed lead to varying degrees of patience.
Further, recent models of intertemporal choice have posited that people use ratios in intertemporal choices \cite{Read2013, MarzilliEricson2015}. 
However, to the best of my knowledge, no study has investigated how explicitly framing time as a ratio can alter patience.
Further although shipping scenarios are a form of intertemporal choice, they differ from how most studies operationalize intertemporal choices.

Across 3 studies I show that by making ratios explicit people are more impatient in intertemporal choices. 
This result holds for intertemporal choices framed as gains, losses, and in an explicit shipping scenario. 
As opposed to other studies which showed that reframed times as dates increases patience, framing times as ratios decreases patience.
Firms wanting to decrease patience in their consumers may want to frame intertemporal choices as ratios as opposed to delays.

@@

Although the majority of intertemporal choice studies involve choices between gains, temporal choices can also take the form of choices between losses \cite{Hardisty2013, Hardisty2015}. 
Although losses have been shown to be a critical moderator of intertemporal preferences cite{Hardisty2013} few studies explore how loses affect intertemporal choices.
Further all studies cited so far have only looked at framing effects of intertemporal choices framed as gains. 
Framing effects which are robust for gains, may have affect losses differently.

@@

%Further most studies investigating framing effects on intertemporal choices are restricted to the domain of gains. 
%Study 2 investigates how framing times as ratios leads to decreased patience in losses. 
%
%Study 3 extends the results from Study 1 and Study 2 to intertemporal choices explicitly framed as shipping scenarios.
%Shipping scenarios are typically displayed as a choice between ``Receive your items in 2 days and pay \$8'' and ``Receive your items in 10 days and pay \$4''
%Although choosing a shipping speed is similar to the previous intertemporal choices there is a subtle, yet possibly significant difference between the two.
%Shipping decisions can be thought of as \textit{paying more now to receive an item sooner} whereas the intertemporal choices shown in Study 2 can be thought of as \textit{paying something smaller now to avoid paying something larger later}.
%This difference in choices  
%

@@

Study 2 extends the results of Study 1 to losses. 
Although most intertemporal choice studies use gains, a large number of real world intertemporal choices involve losses \cite{Hardisty2013}. 
For instance waiting to pay off your credit card incurs greater losses if you wait -- the compounding interest -- than if pay it off immediately.
Intertemporal choices framed as lossed measured in the lab take the form of choices between ``Pay \$100 immediately'' and  ``Pay \$110 in 6 months'' \cite{Hardisty2015}.
